Plot responses to model covariates to inform threshold choices for VOCC

### 2019-08-28 analysis/VOCC/3-fixed-var-response-plots.Rmd
calculate and save optimal values and max predicted biomass from fixed response to climate variables

Species
```{r}
# species <- params$species
# # Species run so far...
 species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

Choose model details
```{r}
covariates <- ""
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
#covariates <- "+muddy+any_rock"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
```

Run all subsequent code...
```{r global_options, include=FALSE}
covs <- gsub("\\+", "-", covariates)
spp <- gsub(" ", "-", gsub("\\/", "-", tolower(species)))

@@

Load Dissolved O2 models
```{r}
rm(
  adult, imm,
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- FALSE
# covariates <- ""

try({
  survey <- c("SYN QCS", "SYN HS", "SYN WCVI", "SYN WCHG")
  model_ssid <- c(1, 3, 4, 16)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult")) adult <- NULL
if (!exists("imm")) imm <- NULL

try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

try({
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

try({
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})

@@

model_list <- list(
  adult = adult, imm = imm,
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

model_list <- model_list[!sapply(model_list, is.null)]
```

Load temperature models
```{r}
rm(adult, imm,
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- FALSE
covariates <- "+muddy+any_rock"
covs <- gsub("\\+", "-", covariates)

try({
  survey <- c("SYN QCS", "SYN HS", "SYN WCVI", "SYN WCHG")
  model_ssid <- c(1, 3, 4, 16)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult")) adult <- NULL
if (!exists("imm")) imm <- NULL

try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

try({
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

try({
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})

temp_model_list <- list(
  adult = adult, imm = imm, 
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

temp_model_list <- temp_model_list[!sapply(temp_model_list, is.null)]
```

Save optimal values

```{r}
td <- list()

for (i in seq_len(length(temp_model_list))) {
  td[[i]] <- fixed_density(temp_model_list[[i]], predictor = "temp")
  #browser()
  if (length(td[[i]])>0) td[[i]]$model <- names(temp_model_list[i])
  if (length(td[[i]])>0) td[[i]]$optimal_temp <- get_optimal_value(td[[i]], xlimits = c(0, 12))
}

tdat <- do.call("rbind", td) %>%
  group_by(model) %>%
  mutate(age = ifelse(grepl("imm", model), "imm", "adult"),
    t_maxy = max(y_hat)) %>% 
  select(model, age, optimal_temp, t_maxy) %>%
  distinct()

do <- list()

for (i in seq_len(length(model_list))) {
 do[[i]] <- fixed_density(model_list[[i]], predictor = "do_mlpl")
 if (length(do[[i]])>0) do[[i]]$model <- names(model_list[i])
 if (length(do[[i]])>0) do[[i]]$optimal_do <- get_optimal_value(do[[i]], xlimits = c(0.5, 6))
}

odat <- do.call("rbind", do) %>%
  group_by(model) %>%
  mutate(age = ifelse(grepl("imm", model), "imm", "adult"),
    do_maxy = max(y_hat)) %>% 
  select(model, age, optimal_do, do_maxy) %>%
  distinct()

params <- full_join(tdat, odat, by=c("model", "age"))
#params <- tdat
params$species <- species
#params$date <- Sys.Date()

other_params <- readRDS(paste0("data/optimal-values-by-species-by-age.rds"))
params <- rbind(other_params, params)
saveRDS(params, file = "data/optimal-values-by-species-by-age.rds")

Build DO plots

```{r}
d <- list()
do_plots <- list()
for (i in seq_len(length(model_list))) {
  d[[i]] <- fixed_density(model_list[[i]], predictor = "do_mlpl")
  if (length(d[[i]]) == 0) {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } else {
    do_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Dissolved O2", xlimits = c(0, 8)) + ggtitle(paste(species, names(model_list[i])))
  }
}
print(do_plots)
```

```{r}
png(
  file = paste0("figs/", spp, "/do-", spp, covs, "-priors-TRUE.png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = do_plots,
  ncol = 2,
  top = grid::textGrob(paste(species))
)
dev.off()
```

Build Temperature plots

```{r}
d <- list()
temp_plots <- list()
for (i in seq_len(length(temp_model_list))) {
  d[[i]] <- fixed_density(temp_model_list[[i]], predictor = "temp")

  if (length(d[[i]]) == 0) {
    temp_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } else {
    temp_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Temperature", xlimits = c(2, 10)) +
      ggtitle(paste(species, names(temp_model_list[i])))
  }
}
print(temp_plots)
```

```{r}
png(
  file = paste0("figs/", spp, "/temp-", spp, covs, "-priors-TRUE.png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = temp_plots,
  ncol = 2,
  top = grid::textGrob(paste(species))
)
dev.off()
```

Load Depth models
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- FALSE
try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey1 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

try({
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey4 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

try({
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})

depth_model_list <- list(
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

depth_model_list <- depth_model_list[!sapply(depth_model_list, is.null)]
```

@@

Plot time-varying effect of trawling at mean depth

```{r}
trawl_plots <- list()
for (i in seq_len(length(depth_model_list))) {
  r <- depth_model_list[[i]]$tmb_obj$report()
  b3 <- r$b_rw_t[, 3]
  yrs <- sort(unique(depth_model_list[[i]]$data$year))
  b_j <- depth_model_list[[i]]$model$par[1:length(yrs)]

@@

### Code for calculation SE on time-varying effects...

```{r eval=FALSE}
# FIXME: need to add to sdmTMB!
r <- m$tmb_obj$report()
summary(m)
yrs <- sort(unique(m$data$year))
.sd <- summary(m$sd_report)
.sd <- as.data.frame(.sd)
.sd$par <- row.names(.sd)
.sd <- .sd[grepl("^b_rw_t", .sd$par), ]
varnames <- colnames(model.matrix(m$time_varying, m$data))

>>>>

Species
```{r}
# species <- params$species
# # Species run so far...
 species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
 species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
 species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

Choose model details
```{r}
covariates <- ""
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
#covariates <- "+muddy+any_rock"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"

# priors <- FALSE
# covariates <- "+muddy+any_rock"
# covs <- gsub("\\+", "-", covariates)
priors <- TRUE
covs <- "-tv-depth"
```

Run all subsequent code...
```{r global_options, include=FALSE}
spp <- gsub(" ", "-", gsub("\\/", "-", tolower(species)))

@@

Load Dissolved O2 models
```{r}
rm(adult, imm,
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16)

try({
  survey <- c("SYN QCS", "SYN HS", "SYN WCVI", "SYN WCHG")
  model_ssid <- c(1, 3, 4, 16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult")) adult <- NULL
if (!exists("imm")) imm <- NULL

try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult_survey1 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey1 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

try({
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult_survey4 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey4 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

try({
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult_survey16 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey16 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey16")) adult_survey16 <- NULL
if (!exists("imm_survey16")) imm_survey16 <- NULL

model_list <- list(
  adult = adult, imm = imm,
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16#, imm_survey16 = imm_survey16
)
model_list <- model_list[!sapply(model_list, is.null)]
```

```{r}
# test load small sdm model to avoid crashing R
try({imm})
# or maybe it's crashing when NaNs produced error goes into density function?
```

Load temperature models
```{r}
rm(adult, imm,
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16)

try({
  survey <- c("SYN QCS", "SYN HS", "SYN WCVI", "SYN WCHG")
  model_ssid <- c(1, 3, 4, 16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult")) adult <- NULL
if (!exists("imm")) imm <- NULL

try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult_survey1 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey1 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

try({
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult_survey4 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey4 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

try({
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey16 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-temp", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey16")) adult_survey16 <- NULL
if (!exists("imm_survey16")) imm_survey16 <- NULL

temp_model_list <- list(
  adult = adult, imm = imm, 
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)
temp_model_list <- temp_model_list[!sapply(temp_model_list, is.null)]
```

```{r}
do <- list()
do_plots <- list()

for (i in seq_len(length(model_list))) {
 do[[i]] <- fixed_density(model_list[[i]], predictor = "do_mlpl")
 if (length(do[[i]])>0) {
   do[[i]]$species <- species
   do[[i]]$model <- names(model_list[i])
   do[[i]]$covs <- covs 
   do[[i]]$optimal_do <- get_optimal_value(do[[i]], xlimits = c(0.5, 6))
   do_plots[[i]] <- 
     plot_mountains(do[[i]], variable_label = "Dissolved O2", xlimits = c(0, 8)) +
        ggtitle(paste(species, names(model_list[i])))
   } else {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  }
}

odat <- do.call("rbind", do) 
if (length(odat)>0) {
  odat <- odat %>% group_by(model) %>%
  mutate(age = ifelse(grepl("imm", model), "imm", "adult"),
    do_maxy = max(y_hat)) %>% 
  select(species, age, model, optimal_do, do_maxy, covs) %>% 
  distinct() 
} else {
  odat <- NULL
}
print(do_plots)
```

```{r}
td <- list()
temp_plots <- list()
for (i in seq_len(length(temp_model_list))) {
  td[[i]] <- fixed_density(temp_model_list[[i]], predictor = "temp")
  if (length(td[[i]])>0) {
    td[[i]]$species <- species
    td[[i]]$model <- names(temp_model_list[i])
    td[[i]]$covs <- covs
    td[[i]]$optimal_temp <- get_optimal_value(td[[i]], xlimits = c(0, 12))
    temp_plots[[i]] <- plot_mountains(td[[i]], variable_label = "Temperature", xlimits = c(2, 10)) +
      ggtitle(paste(species, names(temp_model_list[i])))
  } else {
    temp_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  }
}

tdat <- do.call("rbind", td) 
if (length(tdat)>0) {
  tdat <- tdat %>% group_by(model) %>%
  mutate(age = ifelse(grepl("imm", model), "imm", "adult"),
    t_maxy = max(y_hat)) %>% 
  select(species, age, model, optimal_temp, t_maxy, covs) %>%
  distinct() 
} else {
  tdat <- NULL
}
print(temp_plots)
```

Save optimal values
```{r}
params <- full_join(tdat, odat, by=c("species", "age", "model", "covs"))

other_params <- readRDS(paste0("data/optimal-values-by-species-by-age-tv-depth.rds"))
params <- rbind(other_params, params) 
#%>% select(species, age, model, optimal_temp, t_maxy, optimal_do, do_maxy, covs)
saveRDS(params, file = "data/optimal-values-by-species-by-age-tv-depth.rds")

Save DO plots
```{r}
png(
  file = paste0("figs/", spp, "/do-fixed-", spp, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = do_plots,
  ncol = 2,
  top = grid::textGrob(paste(species))
)
dev.off()
```

Save Temperature plots
```{r}
png(
  file = paste0("figs/", spp, "/temp-fixed-", spp, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = temp_plots,
  ncol = 2,
  top = grid::textGrob(paste(species))
)
dev.off()
```

Load Depth models
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- FALSE
covariates <- "+muddy+any_rock"
covs <- gsub("\\+", "-", covariates)
try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult_survey1 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey1 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL

try({
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult_survey4 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey4 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL

try({
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  adult_survey16 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey16 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})

@@

depth_model_list <- list(
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)
depth_model_list <- depth_model_list[!sapply(depth_model_list, is.null)]
```

@@

Plot time-varying effect of trawling at mean depth
```{r}
trawl_plots <- list()
for (i in seq_len(length(depth_model_list))) {
  r <- depth_model_list[[i]]$tmb_obj$report()
  b3 <- r$b_rw_t[, 3]
  yrs <- sort(unique(depth_model_list[[i]]$data$year))
  b_j <- depth_model_list[[i]]$model$par[1:length(yrs)]

@@

### Code for calculation SE on time-varying effects... 
```{r eval=FALSE}
# FIXME: need to add to sdmTMB!
r <- m$tmb_obj$report()
summary(m)
yrs <- sort(unique(m$data$year))
.sd <- summary(m$sd_report)
.sd <- as.data.frame(.sd)
.sd$par <- row.names(.sd)
.sd <- .sd[grepl("^b_rw_t", .sd$par), ]
varnames <- colnames(model.matrix(m$time_varying, m$data))
